Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-11-03 RMS/final-version/main.tex
polished whole file

%\documentclass[onecolumn]{IEEEtranTIE}
\documentclass[journal]{IEEEtranTIE}
\usepackage{graphicx}
\usepackage[noadjust]{cite}
\usepackage{picinpar}
\usepackage{amsmath}
\usepackage{stfloats}
\usepackage{url}
\usepackage{flushend}
\usepackage[latin1]{inputenc}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{color}
\usepackage{alltt}
\usepackage[hidelinks]{hyperref}
\usepackage{enumerate}
\usepackage{siunitx}
\usepackage{breakurl}
\usepackage{epstopdf}
\usepackage{pbox}

%% My packages
%% \usepackage[cmex10]{amsmath}
%% \interdisplaylinepenalty=2500
\usepackage{algpseudocode}
%% \usepackage{array}
%%\usepackage{dblfloatfix}
%%\usepackage[caption=false,font=footnotesize]{subfig}

\usepackage{tikz}
\usetikzlibrary{arrows.meta}
%% \usepackage{mathabx}

@@

  \thanks{
    Manuscript received November 8, 2015; revised March 30, 2016 and
    July 13, 2016; accepted October 20, 2016. This work was supported
    in part by NSFC Program (No. 91218302, No. 61527812), National
    Science and Technology Major Project (No. 2016ZX01038101), MIIT
    IT funds (Research and application of TCN key technologies) of
    China, and The National Key Technology R\&D Program
    (No. 2015BAG14B01-02).

    J. Liu is with the Department of Computer Science \& Technology,
    Tsinghua University, Beijing 100084, China, and also with LIX,
    \'Ecole Polytechnique, Palaiseau 91120, France (e-mail:
    jiaxiang.liu@hotmail.com).

    M. Zhou is with the School of Software, Tsinghua University,
    Beijing 100084, China (corresponding author; phone:
    +86-10-6277-3275; fax: +86-10-6278-3549; e-mail: zhoumin03@gmail.com).

    X. Song is with the Department of Electrical \& Computer
    Engineering, Portland State University, Portland, OR 97207-0751,
    USA.

    M. Gu and J. Sun are with the School of Software, Tsinghua
    University, Beijing 100084, China.
  }
}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Liu.jpg}}]%
{Jiaxiang Liu} received his B.S. degree from the School of Software,
Tsinghua University, China, in 2010. He is now a co-supervised
Ph.D. candidate between the Department of Computer Science and
Technology, Tsinghua University, China and LIX, \'Ecole Polytechnique,
France. His research interests include formal methods, rewrite systems
and embedded systems.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Zhou.jpg}}]%
{Min Zhou} received his B.S. degree from the Department of
Mathematical Science and Ph.D. degree from the Department of Computer
Science and Technology, Tsinghua University, China, in 2007 and 2014,
respectively. He is now a lecturer at the School of Software, Tsinghua
University. His research interests include model checking, program
analysis and testing.
\end{IEEEbiography}

%% \vspace{-2cm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{X_Song.jpg}}]%
{Xiaoyu Song} () received the Ph.D. degree from the University of
Pisa, Italy, in 1991. From 1992 to 1998, he was on the faculty at the
University of Montreal, Canada. He joined the Department of Electrical
and Computer Engineering at Portland State University in 1998, where
he is now a professor. He was an editor of IEEE Transactions on VLSI
Systems and IEEE Transactions on Circuits and Systems. He was awarded
an Intel Faculty Fellowship from 2000 to 2005. His research interests
include formal methods, design automation, embedded systems and
emerging technologies.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Gu.jpg}}]%
{Ming Gu} is a professor at the School of Software, Tsinghua
University and vice-director of Ministry of Education Key Laboratory
of Information Security, China. Her research interests include
software formal methods, software trustworthiness and middleware
technology.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Sun.jpg}}]%
{Jiaguang Sun} is a professor and dean of the School of Information
Science and Technology in Tsinghua University, China. He is also a
member of the Chinese Academy of Engineering, director of Ministry of
Education Key Laboratory of Information Security, and director of
Tsinghua National Laboratory for Information Science and Technology,
China. His research interests include computer graphics,
computer-aided design, formal verification of software, software
engineering, and system architecture.
\end{IEEEbiography}

>>>>

%\documentclass[onecolumn]{IEEEtranTIE}
\documentclass[journal]{IEEEtranTIE}
\usepackage{graphicx}
\usepackage[noadjust]{cite}
\usepackage{picinpar}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{stfloats}
\usepackage{url}
\usepackage{flushend}
\usepackage[latin1]{inputenc}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{color}
\usepackage{alltt}
\usepackage[hidelinks]{hyperref}
\usepackage{enumerate}
\usepackage{siunitx}
\usepackage{breakurl}
\usepackage{epstopdf}
\usepackage{pbox}

%% My packages
%% \usepackage[cmex10]{amsmath}
%% \interdisplaylinepenalty=2500
%% \usepackage{algpseudocode}
%% \usepackage{array}
%%\usepackage{dblfloatfix}
%%\usepackage[caption=false,font=footnotesize]{subfig}

%% \usepackage{tikz}
%% \usetikzlibrary{arrows.meta}
%% \usepackage{mathabx}

@@

  \thanks{ 
    Manuscript received November 8, 2015; revised March 30,
    2016 and July 13, 2016; accepted October 20, 2016. This work was
    supported in part by NSFC Program (No.\ 91218302, No.\ 61527812,
    No.\ 91218302), National Science and Technology Major Project
    (No.\ 2016ZX01038101), MIIT IT funds (Research and application of
    TCN key technologies) of China, and The National Key Technology
    R\&D Program (No.\ 2015BAG14B01-02).

    J.\ Liu is with the Department of Computer Science \& Technology,
    Tsinghua University, Beijing, China 
    \hide{, and also with LIX,
    \'Ecole Polytechnique, Palaiseau 91120, France} (e-mail:
    jiaxiang.liu@hotmail.com).

    M.\ Zhou is with the School of Software, Tsinghua University,
    Beijing 100084, China (corresponding author; phone:
    +86-10-6277-3275; fax: +86-10-6278-3549; e-mail:
    zhoumin03@gmail.com).

    X.\ Song is with the Department of Electrical \& Computer
    Engineering, Portland State University, Portland, OR 97207-0751,
    USA.

    M.\ Gu and J.\ Sun are with the School of Software, Tsinghua
    University, Beijing 100084, China.

    J.\ Liu, M.\ Zhou, M.\ Gu and J.\ Sun are also with Key Laboratory
    for Information System Security, Ministry of Education, China, and
    Tsinghua National Laboratory for Information Science and
    Technology, China.  
  }  
}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Liu.jpg}}]%
{Jiaxiang Liu} received his B.S.\ degree in computer software from
Tsinghua University, China in 2010. He is now a Ph.D.\ candidate in
the Department of Computer Science and Technology, Tsinghua
University, China. His research interests include formal methods,
rewrite systems and embedded systems.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Zhou.jpg}}]%
{Min Zhou} received his B.S.\ degree from the Department of
Mathematical Science and Ph.D.\ degree from the Department of Computer
Science and Technology, Tsinghua University, China in 2007 and 2014,
respectively. He is now a lecturer at the School of Software, Tsinghua
University. His research interests include model checking, program
analysis and testing.
\end{IEEEbiography}

%% \vspace{-2cm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{X_Song.jpg}}]%
{Xiaoyu Song} () received the Ph.D.\ degree from the University of
Pisa, Italy, in 1991. From 1992 to 1998, he was on the faculty at the
University of Montreal, Canada. He joined the Department of Electrical
and Computer Engineering at Portland State University in 1998, where
he is now a professor. He was an editor of IEEE Transactions on VLSI
Systems and IEEE Transactions on Circuits and Systems. He was awarded
an Intel Faculty Fellowship from 2000 to 2005. His research interests
include formal methods, design automation, embedded systems and
emerging technologies.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Gu.jpg}}]%
{Ming Gu} is a professor at the School of Software, Tsinghua
University, China. She is also vice-director of Key Laboratory for
Information System Security, Ministry of Education, China. Her
research interests include software formal methods, software
trustworthiness and middleware technology.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Sun.jpg}}]%
{Jiaguang Sun} is a professor and dean of the School of Information
Science and Technology in Tsinghua University, China. He is also a
member of the Chinese Academy of Engineering, director of Ministry of
Education Key Laboratory for Information System Security, and director
of Tsinghua National Laboratory for Information Science and
Technology, China. His research interests include computer graphics,
computer-aided design, formal verification of software, software
engineering, and system architecture.
\end{IEEEbiography}
